---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


## Overview

Author: Yong-Han Hank Cheng

This package provides functions for:
1. Preprocessing data.
2. Clustering with K-means or hierarchical clustering.
3. Classification with random forest. 

## Installation

```{r, eval = FALSE}
# Install the package from GitHub
devtools::install_github("yhhc2/machinelearnr")
```

```{r}
# Load package
library("machinelearnr")
```

## Usage

Visit the package's website for function reference: <https://yhhc2.github.io/machinelearnr/>

## Examples

All functions with example code is run in this section. The functions are
listed below in alphabetical order with example code to illustrate
how each function should be used. The example code should be very similar
to the example code in the function reference. 

To see detailed descriptions for each function, please visit the package's website.

## Examples for clustering

### AutomatedCompositePlotting()



## Examples for classification


